---
title: "Text Analysis"
description: |
  Analysis of the Netflix shows
author: Max Feng
date: March 5, 2025
format: html
execute:
  echo: TRUE
---

The link to the TidyTuesday resource is: <https://github.com/rfordatascience/tidytuesday/blob/main/data/2021/2021-04-20/readme.md>

The original data comes from: <https://www.kaggle.com/datasets/shivamb/netflix-shows>

Part I: String Data Wrangling

```{r}
library(dplyr, warn.conflicts = FALSE)
library(stringr)
library(ggplot2)
netflix_titles <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2021/2021-04-20/netflix_titles.csv', show_col_types = FALSE)
new_netflix_titles <- netflix_titles |>
  mutate(show_id_num = str_sub(show_id, 2, )) |>
  mutate(title_length = str_length(title)) |>
  mutate(us_show = str_detect(country, "United States"))
love_titles <- netflix_titles |>
  filter(str_detect(title, "\\bLove\\b"))
shows_at_2000s <- netflix_titles |>
  filter(str_detect(release_year, "200[0-9]$"))
comedy_shows <- netflix_titles |>
  filter(str_detect(listed_in, "\\bComedies\\b"))
comedies_only <- comedy_shows |>
  filter(str_detect(listed_in, "(?<! )Comedies(?!,)"))
```

Part II: Distribution of Title Lengths of the Shows

```{r}
ggplot(new_netflix_titles, aes(x = title_length)) +
  geom_histogram(binwidth = 3) +
  labs(title = "distribution of title lengths of shows", 
       x = "length of titles")
```

In this analysis, I made a histogram of the distribution of title lengths of the shows in Netflix. The x-axis is the value of different lengths, and the y-axis is the number of shows at a certain value of the title length. In general, the distribution is right-skewed. Most shows have the title length between 8-16 characters. Very few shows have the title length greater than 50 characters.

Part III: Rating Systems of the Shows

```{r}
ggplot(netflix_titles, aes(x = rating, fill = rating)) +
  geom_bar() +
  geom_label(stat = "count", aes(label = after_stat(count))) +
  labs(title = "distribution of the rating systems of shows", 
       x = "rating systems")
```

In this analysis, I made a bar plot that analyzes the number of Netflix shows with different rating systems. The x-axis is the different rating systems and the y-axis is the number of shows that use a specific rating system. TV-MA has the most uses in shows, with 2863 shows that fall into this category. Very few shows use NC-17, TV-Y7-FV, and UR.
